---
title: "A3 Incarceration Jayden Set"
author: "Jayden Set"
date: "3/2/2022"
output: html_document
---
```{r setup1, include=FALSE}
library(tidyverse)
library(dplyr)
library(lintr)
library(styler)
library(maps)
library(mapproj)
```

```{r setup, include=FALSE}
source("analysis.R")
```
## Intro & Summary
In the report I will be looking at Vera's data to analyze the incarceration trends csv file. This specific study has focused on the overall jail population in Counties across the US, they most specifically focused on New York but their are many others as well. It is important to understand that many people in jail could be innocent, and along with that, you will notice how diverse these jail's may be.

### Exploritory Problems using DPLYR functions 
What counties have the highest black jail population?

`r location_highest_black`



What county has the highest black population

`r county_highest_black`



Who has the highest ratio of black people jailed compared to black pop

`r highest_ratio_black`



 County with the highest black vs white differential jailed 

`r county_highest_black_white_ratio`



Find the top 5 locations with highest black jail population rate

`r top_5_locations`
